Simulating the Lipkin-Meshov-Glikov model on a classical computer

### 2023-05-30 doc/paper.tex
Adding the last bit of description about quantum gates
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

\begin{enumerate}
	\item[\textbf{I}.] \textbf{Identity gate}
		\begin{equation*}
			I = \begin{pmatrix}
			1 & 0 \\
			0 & 1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{II.}] \textbf{Pauli-X gate}
		\begin{equation*}
			X = \begin{pmatrix}
			0 & 1 \\
			1 & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{III.}] \textbf{Pauli-Y gate}
		\begin{equation*}
			Y = \begin{pmatrix}
			0 & -i \\
			i & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{IV.}] \textbf{Pauli-Z gate}
		\begin{equation*}
			Z = \begin{pmatrix}
			1 & 0 \\
			0 & -1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{V.}] \textbf{Hadamard gate}
		\begin{equation*}
			H = \frac{1}{\sqrt{2}} \begin{pmatrix}
			1 & 1 \\
			1 & -1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{VI.}] \textbf{Phase gate}
		\begin{equation*}
			S = \begin{pmatrix}
			1 & 0 \\
			0 & i \\
		\end{pmatrix}.
	\end{equation*}
		For a single qubit, application of each of these matrices represents a rotation of the qubit on the \textit{Bloch sphere (Fig. 1)}. (For more details, take a look at [Hundt, p.56] or [Nielsen, p.19])

@@

@@

As the first part of our project, we prepared single qubits in their basis state $|0>$ and $|1>$. The effect each gate has on one of the states is presented below, presented in the order the gates were listed in \textbf{Section II}. The results of applying the gates are:

		\begin{enumerate}
			\item[\textbf{I}. Identity gate] 
				The result of applying both the $\sigma_0$ gate to both $|0>$ and $|1>$ results in the exact same states, as the identity gate is simply the identity matrix. Presented using matrices and vectors, the results can be written: 
				\[
				I \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				1 & 0 \\
				0 & 1
				\end{pmatrix} \\ \\ \\
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				\]

>>>>

\begin{enumerate}
	\item[\textbf{I}.] \textbf{Identity gate} \\
		This gate does nothing to the state of the qubit, as if a gate never was applied to the qubit in the first place.
		\begin{equation*}
			I = \begin{pmatrix}
			1 & 0 \\
			0 & 1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{II.}] \textbf{Pauli-X gate} \\
		The Pauli-X gate, also known as the quantum NOT-gate, flips the probability amplitudes $\alpha$ and $\beta$, meaning that these values swap place in the state vector. 
		\begin{equation*}
			X = \begin{pmatrix}
			0 & 1 \\
			1 & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{III.}] \textbf{Pauli-Y gate} \\
		The action of the Pauli Y gate can be described as the mapping of $|0>$ to $i|1>$ and $|1>$ to $i¦0>$. The action of the gate can also be viewed as a rotation of the state of the qubit around the y-axis of the Bloch sphere by 180 degrees.
		\begin{equation*}
			Y = \begin{pmatrix}
			0 & -i \\
			i & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{IV.}] \textbf{Pauli-Z gate} \\
		The Pauli Z gate flips the phase of $|1>$ to $-|1>$ while leaving $|0>$, meaning it flips the relative phase of the qubit. 
		\begin{equation*}
			Z = \begin{pmatrix}
			1 & 0 \\
			0 & -1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{V.}] \textbf{Hadamard gate} \\
		The result of applying the Hadamard gate to either $|0>$ or $|1>$ is a qubit in a super position of both states, with both the basis states having a 50\% of occuring. The result is the exactly the same, independent of which of the basis states the qubit is prepared in.
		\begin{equation*}
			H = \frac{1}{\sqrt{2}} \begin{pmatrix}
			1 & 1 \\
			1 & -1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{VI.}] \textbf{Phase gate} \\
		The Phase gate, when applied to a qubit, represent the rotation of the second part of a qubit state vector corresponding to $|1>$ by 90 degrees around the z-axis of the bloch sphere.

		\begin{equation*}
			S = \begin{pmatrix}
			1 & 0 \\
			0 & i \\
		\end{pmatrix}.
	\end{equation*}
		For a single qubit, application of each of these matrices represents a rotation of the qubit on the \textit{Bloch sphere (Fig. 1)}. (For more details, take a look at [Hundt, p.56] or [Nielsen, p.19])

@@

	\item[\textbf{VII.}] \textbf{CNOT-gate} \\
\end{enumerate}

@@

As the first step of our project, we prepared single qubits in their basis state $|0>$ and $|1>$ and studied the result the application of the various quantum gates had on these one qubit systems. The effect each gate had on the basis states is presented below in the order the gates were listed in \textbf{Section II}. The results of applying the gates are:

		\begin{enumerate}
			\item[\textbf{I}. ] Identity gate \\
				The result of applying both the $\sigma_0$ gate to both $|0>$ and $|1>$ results in the exact same states, as the identity gate is simply the identity matrix. Presented using matrices and vectors, the results can be written.
				\[
				I \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				1 & 0 \\
				0 & 1
				\end{pmatrix} \\ \\ \\
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				\]

			\item[\textbf{II}. ] Pauli-X gate \\
				The application of the Pauli X gate result in flipping of the probability amplitudes of the qubit, resulting in $\alpha$ and $\beta$ swapping places in the qubit. 
				\[
				I \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				0 & 1 \\
				1 & 0
				\end{pmatrix} \\ \\ \\
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\beta \\
				\alpha
				\end{pmatrix}
				\]

				Preparing a qubit in state |0> and applying the quantum NOT-gate results in state |1>.

			\item[\textbf{I}. ] Pauli-X gate \\
